\chapter {Future Work}
\begin{enumerate}
\item \textbf{Auto-complete feature in the editor :} \newline
Currently, this feature is absent in our version of CodeMirror implemented in the Advanced
HTML Xblock . It can be implemented in the future where a user will be shown a list of
options of the probable keywords on the basis of a keystroke.
\newline\newline  \textbf{Reference:} [\url{https://codemirror.net/demo/complete.html}]
\item \textbf{Setting a common CSS for an entire course :} \newline
Presently, if a course author wants to have a unified visual theme for all the content in a particular
course, he/she would have to manually apply the CSS style to each and every unit in the html
code. To make this easier we can have a common CSS file which will be automatically
fetched and imported for every unit in that course as per the settings of the course. One
possible way of implementing it would be making changes on the Django backend of that
particular course to fetch that CSS file from the \textbf{ “Files \& uploads”} section present for every
course in Open edX platform.
\item \textbf{Additional settings in the Xblock :}\newline
At present our Xblock has two options in the settings tab. Display name and Live preview
toggle. Some other features that can be added are :
\begin{itemize}
\item An option for selecting a dark/light theme for the editor to enhance the user experience
even more.
\item Enable a draggable partition interface so that users can adjust the size of the editor
window and the preview windows as desired.
\end{itemize}
\end{enumerate}