\documentclass[a4paper, twosided, openany]{memoir}
\usepackage{hyperref}
\hypersetup{
	colorlinks,
	   linkcolor={black},
           citecolor={black},
           urlcolor={blue}
}
\usepackage{graphicx}

\setlrmarginsandblock{3cm}{2.5cm}{*}
\setulmarginsandblock{2.5cm}{2.5cm}{*}
\checkandfixthelayout
\setlength{\evensidemargin}{\oddsidemargin}

\begin{document}

\pagestyle{plain}
\chapterstyle{demo3}
\title{Advanced HTML XBlock for Open EdX platform}
\date{\today}

\frontmatter

%\maketitle

\chapter*{Certificate of Approval}

\begin{center}
\textsc{\LARGE Summer Internship 2018 Project}\\
\bigskip
\textsc{\Large Approval Certificate}\\
\bigskip
\textsc{ Department of Computer Science \& Engineering, IIT Bombay}\\
\textsc{--------------------------------------------------------------------------------------------------}\\
\bigskip\bigskip\bigskip\bigskip\bigskip\bigskip

The project entitled "Advanced HTML XBlock for Open EdX platform" submitted by Mr. Ashutosh Sathe, Mr. Srijan Roy Choudhury and Ms. Pravallika Podugu is approved for Summer Internship 2018 programme for 16th May 2018 to 6th July 2018, at Department of Computer Science and Engineering, IIT Bombay
\end{center}

\chapter*{Declaration}
\begin{center}

\end{center}

\chapter*{Abstract}
The project focuses on enhancing the open edx html component. Current html component does not
allow a fully fledged html, css and javascript content to be added in course. Also the html editor of
the current component is not very user friendly and lacks some fundamental functionalities such as
code indentation, code folding etc. Our first approaach was to modify openedx system itself and
thus changing the html editor for all users. Lateron we decided to move to devloping an xblock for
this and hence making it optional. We also added extra features to enahance the functionality of
xblock. These extra features include live previewing the html content along with editor.\newline
\par\fancybreak{$***$}\par

% Using newpage instead of pagebreak keeps the vertical alginment
% pagebreak will spread the content all over the page and that is why we had center alignment before
% This completely fixes it
\newpage

\chapter*{Acknowledgement}
	We, the summer interns of this group, are overwhelmed in all humbleness and
gratefulness to acknowledge our deep gratitude to all those who have helped us put
our ideas to perfection and have assigned tasks well above the level of simplicity and
into something concrete and unique.
We, wholeheartedly thank Prof. D.B. Phatak for having faith in us, selecting us to be
a part of his valuable project and for constantly motivating us to do better.
We thank Miss Kalpana Kannan for providing us the opportunity to work on this
project.We are also very thankful to our mentors Mr. Hitesh Murkute and Mr. Sachin R Shirsat
for their valuable suggestions. They were always there to show us the right track when needed help.
With help of their brilliant guidance and encouragement, we all were able to complete
our tasks properly and were up to the mark in all the tasks assigned. During the
process, we got a chance to see the stronger side of our technical and nontechnical
aspects and also strengthen our concepts.
Last but not the least, we wholeheartedly thank all our other colleagues working in
different projects under Prof. D.B Phatak for helping us evolve better with their critical advice.\newline
\par\fancybreak{$***$}\par
\newpage

\tableofcontents

\mainmatter

\include{part1}
\include{part2_0}
\include{part3}
\include{devstack}
\include{part2_1}
\include{advancedhtmlxblock}
\include{conclusion}
\include{futurework}
\include{part2_2}
\end{document}